Making Sequential Programs Deterministic

### 2019-03-28 experiments.tex

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Benchmark & Recall? & Error message source & # annotations & Type of annotation added & Comments \\ \hline
        P1 &  &  &  &  &  \\
        P2 &  &  &  &  &  \\
        P3 &  &  &  &  &  \\ 
        P4 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\ 
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P9 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P11 &  &  &  &  &  \\
        P12 &  &  &  &  &  \\
        P13 &  &  &  &  &  \\
        P14 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P16 &  &  &  &  &  \\
        P17 &  &  &  &  &  \\
        P18 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{4cm}|p{2cm}|p{1.5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg & \#annotations & Annotation type  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible &  &   \\
        P2 & MI &  &  &  &  \\
        P3 & Yes & DateTimeZone.java: [475,15] &  return type incompatible&  &  \\ 
        P4 & MI &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\
        P7(test error) & Yes & checker/ tests/ determinism/P71.java: 5 & return type incompatible &  &  \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible &  &  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible &  &  \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible &  &  \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible & &  \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P9 & MI &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P11 & MI &  &  &  &  \\
        P12 & MI &  &  &  &  \\
        P13 & crash &  &  &  &  \\
        P14 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible &  &  \\
        P17 & Yes &  &  &  &  \\
        P18 & src &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\ \hline
    \end{tabular}
\end{table}
